### 2015-11-30 pics/blue.tex
change peak description in red and blue clusters

\draw[thick] (axis cs:1.45,0.003) arc [radius=0.80cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
     at (axis cs:1.1,0.0038) {};

\draw[thick] (axis cs:2.00,0.0078) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
     at (axis cs:2.0,0.0080) {};

\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
     at (axis cs:2.70,0.0010) {};

>>>>

\draw[thick] (axis cs:1.45,0.003) arc [radius=0.80cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]90:{\small \textbf{(a)} across shells}}]
     at (axis cs:1.1,0.0038) {};

\draw[thick] (axis cs:2.00,0.0078) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]10:{\small \textbf{(b)} same shell}}]
     at (axis cs:2.0,0.0080) {};

\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]92:{\small \textbf{(c)} across shells}}]
     at (axis cs:2.70,0.0010) {};

### 2015-11-30 pics/rot.tex
change peak description in red and blue clusters

\draw[thick] (axis cs:1.40,0.007) arc [radius=0.77cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
     at (axis cs:1.0,0.0080) {};

\draw[thick] (axis cs:1.90,0.0120) arc [radius=0.55cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
     at (axis cs:1.9,0.0125) {};

\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
     at (axis cs:2.70,0.0010) {};

>>>>

\draw[thick] (axis cs:1.40,0.007) arc [radius=0.77cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]90:{\small \textbf{(a)}\\ across shells}}]
     at (axis cs:1.0,0.0080) {};

\draw[thick] (axis cs:1.90,0.0120) arc [radius=0.55cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]10:{\small \textbf{(b)} same shell}}]
     at (axis cs:1.9,0.0125) {};

\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
\node[pin={[pin distance=0.2cm]92:{\small \textbf{(c)} across shells}}]
     at (axis cs:2.70,0.0010) {};
